\section{Recommendation}

\begin{frame}[fragile]{Recommended websites}
	\begin{itemize}
		\item Sub websites from \href{https://stackexchange.com/}{stack exchange} like \href{https://stackoverflow.com/}{Stackoverflow} and \href{https://math.stackexchange.com/}{Math Stackexchange}
		\item \href{https://github.com/}{Github}
		\item \href{https://wiki.archlinux.org/}{Arch wiki}
	\end{itemize}
\end{frame}

\begin{frame}[fragile]{The Correct Way to Use Search Engines}
	\begin{itemize}
		\item Use reliable search engines for technical queries, e.g., \textbf{Google}, \textbf{Perplexity}, \textbf{Bing}.
		\item Avoid region-limited engines for technical searches (e.g., \textbf{Baidu}) due to irrelevant advertisements or outdated documentation.
		\item Use advanced search operators for more precise results:
			\begin{itemize}
				\item \texttt{site:stackoverflow.com <query>} → search only on StackOverflow
				\item \texttt{filetype:pdf <query>} → search for PDF files
				\item \texttt{"exact phrase"} → search exact matches
			\end{itemize}
		\item Use programming-specific sources:
			\begin{itemize}
				\item GitHub search: find code examples and projects
				\item StackOverflow: find solutions to common errors
				\item Official documentation: most reliable, do always verify with source
			\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}[fragile]{The Correct Way to Use AI}
    \begin{itemize}
        \item \textbf{Define the problem clearly:}
        \begin{itemize}
            \item Be specific about your goal, the role of AI in this process and expected output.
            \item Break complex tasks into smaller, manageable sub-tasks.
        \end{itemize}

        \item \textbf{Validate AI output:}
        \begin{itemize}
            \item Cross-check AI suggestions with official documentation, scientific sources, or authoritative references.
            \item Treat AI output as a recommendation, not absolute truth.
        \end{itemize}

        \item \textbf{Leverage AI effectively:}
        \begin{itemize}
            \item Avoid blindly copying output; understand and adapt it, else, you learn nothing from this chat but waste your time.
            \item Make sure you understand what AI is doing. AI may create dangerous cmd and ruin up your env.
            \item Don't abuse AI in hard homework. Most homework is deliberately designed to help you understand the course content.
        \end{itemize}

        \item \textbf{Maintain privacy and security:}
        \begin{itemize}
            \item Do not share sensitive data unless you trust the platform.
            \item Prefer anonymized or synthetic examples when possible.
        \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}[fragile]{The Correct Way to Use AI}
    \begin{itemize}
			\item Google Gemini provide Pro model for free for 12 months after college verification.
			\item Google AI Studio can use all google model for free
			\item Chatgpt and Gemini deepresearch is especially helpful when you want to learn a field you don't know. It is a very good tools when you are doing survey in research.
			\item Qwen-code, gemini-cli is free agent coding tools you can use.
    \end{itemize}
\end{frame}
